|

### 2025-05-04 doc/declaration.tex
Declaration - signature

\section*{Declaration of Originality}

I hereby declare that the present seminar paper and the work reported herein was composed by and originated entirely from me without any help. All sources used from published or unpublished work of others are reported in the list of references. All parts of my work that are based on others’ work are cited as such.

This seminar paper has not been submitted for any degree or other purposes, neither at the Humboldt-Universität zu Berlin nor at any other university or college.

\vspace{20mm}

Berlin, \hrulefill

\vspace{30mm}

\hrulefill \\
Name and surname \hspace{20mm} Signature

>>>>

\section*{Declaration of Academic Honesty}

I, Max Mustermann, hereby declare that I have not previously submitted the present work for other examinations. I wrote this work independently. All sources, including sources from the Internet, that I have reproduced in either an unaltered or modified form (particularly sources for texts, graphs, tables and images), have been acknowledged by me as such.

I understand that violations of these principles will result in proceedings regarding deception or attempted deception.

\vspace{2cm}

\rule{60mm}{0.4pt}

\vspace{0.5cm}

\text{Max Mustermann}

Berlin, \today
